PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-21 paper.tex
Mention the MMDB dataset

One of the most interesting datasets is the \emph{Multimodal Dyadic Behavior
Dataset} (\emph{MMDB},~\cite{rehg2013decoding}). It comprises of 160 sessions of
3 to 5 minute child-adult interactions. During these interactions, the
experimenter plays with toddlers (1.5 to 2.5 years old) in semi-structured ways
which was designed to
elicit a broad range of social behaviors

\todo[inline]{look at child-child datasets!}

>>>>

One interesting dataset is the \emph{Multimodal Dyadic Behavior
Dataset} (\emph{MMDB},~\cite{rehg2013decoding}). It comprises of 160 sessions of
3 to 5 minute child-adult interactions. During these interactions, the
experimenter plays with toddlers (1.5 to 2.5 years old) in semi-structured ways.
The dataset includes video streams of the faces and the room, audio, physiological data
(electrodermal activity) as well as manual annotations of certain behaviours
(like gaze to the examiner, laughter, pointing). The lack of calibration and camera positioning
information in the dataset limits the possibilities of automatically extracting and
labelling key interaction features (like facial expressions or joint gaze). Besides,
this dataset focuses on very young children with in adult-driven interactions,
and as such does not include any episodes of naturally-occurring social
interactions between peers.

\todo[inline]{look at other child-child datasets!}
\todo[inline]{mention research on deep-learning to diagnostic autism}
